### 2023-02-26 tex/paper-acts/main.tex
Update paper to include all simulation runs so far

\documentclass{article}
\usepackage{babel}
\usepackage[includefoot]{geometry}
\usepackage{/home/user1/code/tex/sty}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{floatrow}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[backend=bibtex]{biblatex}
\addbibresource{bib.bib}
\floatsetup[figure]{objectset=centering}
\floatsetup[subfigure]{objectset=centering}
\hypersetup{colorlinks=true,citecolor=black,linkcolor=black}
\setlength{\parindent}{0pt}
\title{Research Report}
\author{Agustin Romero\thanks{ar1@stanford.edu}}

\newcommand{\pic}[2]{\beg{center}{\includegraphics[height=#1]{#2}}}

\newcommand{\figpic}[3]{
\begin{figure}[H]
\begin{center}
\pic{#1}{#2}
\caption{#3}
\end{center}
\end{figure}}

\newcommand{\figtab}[3]{
\begin{table}[H]
\begin{tabular}{#1}
#2
\end{tabular}
\caption{#3}
\end{table}}

\n{abseta}{$|\eta|<$}
\n{ttbar}{$t\bar{t}$~}
\n{qqbar}{$q\bar{q}$~}
\newcommand{\romax}[0]{_{\textrm{max}}}
\newcommand{\romin}[0]{_{\textrm{min}}}
\newcommand{\pt}[0]{p_\textrm{T}}

\begin{document}

\maketitle

\section{Introduction}

The purpose of this paper is to fully describe the research to simulate \ttbar collisions in the Open Data Detector, perform vertex and track reconstruction in ACTS, then find parameters that achieve highest tracking efficiency. This includes the method of research, results, and discussion on what succeeded and what failed to achieve the research goal.

\section{Background}

ATLAS analyses use \abseta~2.5. After the HL-LHC upgrade, ATLAS will use \abseta~4. The goal of this research is to improve the efficiency of tracking and reconstruction, both in accuracy of reconstruction and computational time efficiency.

\subsection{pp at high $|\eta|$}

\subsection{Detector ``transition regtion''}

It is difficult for the CKF algorithm to reconstruct tracks which pass through the barrel strips into the end strips.

\figpic{5cm}{2.png}{Example of a track which passes from the barrel to the end cap. As $|\eta|$ lowers the track's points rightward in this diagram. These tracks are more difficult to reconstruct.}

\figpic{5cm}{3.png}{Plot of track fake rate as a function of eta. In the transition region, there is a spike in fake rate, indicating worse performance by the CKF algorithm.}

\section{Method}

The motivation is to apply track reconstruction to separate parts of the detector. One set of parameters was be optimized for the end cap, and another set of parameters for the barrel.

% \figpic{5cm}{1.png}{Concept of the optimization procedure. Optimize reconstruction parameters for the end cap, and again for the barrel.}

In simulation, scattering events have more simultaneous collisions than soft scattering. \ttt{vx} and \ttt{vy} have high precision, $\pm 16 \mu m$. \ttt{vz} has low precision, $\pm 100 mm$. The most important distributions are Efficiency vs. $\eta$, Efficiency vs. $p_T$. Efficiency vs. $\phi$ is not important. ``Restructed track candidates'' refers to reconstructed track seeds. ``Truth matched'' refers to the number of tracks matched to truth matched. The hits from the pile up events that are placed in tracks are called ``fake.'' The low momentum tracks won't travel as far through the detector, so their reconstruction is statistically less likely because those tracks have significantly less data available to be reconstructed. The cutoff for $p_T$ is $>$ 10 MeV. Sometimes a 1 GeV cutoff is also used. ``Duplication'' refers to two tracks which are linked to the same particle.

\section{Simulation}

\subsection{Detector}

The magnetic field is a solenoid magnet. The magnetic field applies passive material only. rmin = 1160 mm, rmax = 1200 mm, 3 m long. The magnetic field used is not identical to the field used by physics analyses. The passive material is defined as the material from $x_0$ < 2, $\lambda_0$ < 0.42, and $|eta|$ < 4. The detector is divided into the following components: beam pipe, Pixels, PST, short strips, long strips, solenoid. The pixel material is divided into the following material. The detector geometry used was the Open Data Detector. For historical background, in 2008 the reconstruction algorithms used an interaction region which was Gaussian, 5.6 cm in the beam axis, and 15 $\mu$m transverse to the beam \cite{Piacquadio2008}.

\begin{itemize}
\item Four cylindrical barrel layers of radii 34 mm, 70 mm, 116 mm, 172 mm
\item Barrel: 14 sensors per stave, cooling pipe surrounded by carbon foam, 2492 total
\item Pixel endcaps: disks at ±z 620 mm, 720 mm, 840 mm, 980 mm, 1120 mm, 1320 mm 1520 mm
\item Rings: 2 rings: 24, 36 modules, 420 sensors per endcap
\end{itemize}

Short strips. Carbon foam body with titanium cooling pipe. The short strip material is divided into the following material.

\begin{itemize}
\item Four barrel layers at r 260 mm, 360 mm, 500 mm, 660 mm
\item 40 to 102 staves, 21 sensors each
\item Endcaps disks at ±z 1300 mm, 1550 mm, 1850 mm, 2200 mm, 2550 mm, 2950 mm
\item Three rings of 42, 756 sensors in total
\end{itemize}

The long strip material is conventional strip sensors in stereo pairs. The long strip material is divided into the following material.

\begin{itemize}
\item Two barrel layers at r 820 mm, 1020 mm, 60/80 staves of 21 sensors
\item Silicon sensors on kapton boards, carbon foam blocks, titanium cooling pipes
\item Endcaps disks at ±z 1300 mm, 1600 mm, 1900 mm, 2250 mm, 2600 mm, 3000 mm
\item Two rings of 48×2 sensors
\end{itemize}

A \ita{sequence} is an ordered list of algorithms beginning at event generation, through CKF reconstruction, and ending at the CKF efficiency analyzer. A \ita{trial} is one sequence which generates only one event using one set of parameters. A \ita{score} is a number calculated given the efficiencies from one trial.

\figtab{l l}{Pileup & 10\\
Vertex x-axis $\sigma$ [mm] & 0.0125\\
Vertex y-axis $\sigma$ [mm] & 0.0125\\
Vertex z-axis $\sigma$ [mm] & 55.5\\
Vertex t-axis $\sigma$ [ns] & 5}{Parameters used for event generation of vertices.}

% \figtab{l l}{Truth Seed Range $\pt$ [MeV] & 500\\
% r [mm] & 200\\
% \Delta r & Optimized from }

The following equations are used to evaluate the performance of the CKF algorithm. The default parameters used for tracking is used below. Most of these parameters were originally hand tuned. Next, they will be optimized.

\subsection{Event Generation}

\qqbar $\rightarrow$ \ttbar events were simulated at energy 14 TeV, with 140 pileup particles, using Pythia, and tracked using ACTS.

The event generator used was Pythia.

\subsection{Propagation}

Fatras was used to simulate particle propagation through the detector medium and enegy deposition. FATRAS will always remove neutral particles in its propagation. The ``geometry selection file'' is used for space point geometry selection.

\subsection{Kalman Filter algorithm}

\subsection{Seed finding}

The default seeding algorithm is used, which uses no truth information. The seeding algorithm constructs track seeds from space points. The seeding algorithm has these steps:

\begin{enumerate}
\item Within the inner detector, select the first three layers.
\item Select one point in layer 2 that has been assigned to $\leq$ $MaxSeedPerSpM$ number of seeds.
\item Search for one point in layer 1, and one point in layer 3 that that would be compatible as a seed.
\item Add one seed with those three points to the list of seeds.
\end{enumerate}

\subsection{Track fitting}

\subsection{Track finding}

The truth seed selector selects truth particles to be used as seeds of the reconstruction track fitter and reconstruction track finder. The truth particle can be selected with the following parameters:

\begin{enumerate}
\item Minimum and maximum distance to from the origin along transverse plane
\item Minimum and maximum distance from the origin along z
\item Min (max) $\phi$
\item Min (max) $\eta$
\item Min (max) $|\eta|$
\item Min (max) $\pt$.
\item Min (max) number of hits. 
\item Whether to keep neutral particles.
\end{enumerate}

\subsection{Evaluation}

These are equations used for evaluating the CKF reconstruction algorithm. Specifically we are interested in \eqref{score}, \eqref{eff}, \eqref{trackfakerate}, and \eqref{trackduplicaterate}.

\e{\label{eff}\rom{Particle efficiency}=\fr{\rom{Number of matched particles}}{\rom{Number of true particles}}}

\e{\rom{Particle fake rate}=\fr{\rom{Number of unmatched seed particles}}{\rom{Number of seed particles}}}

\e{\rom{Particle duplicate rate}=\fr{\rom{Nmber of duplicate particles}}{\rom{Number of true particles}}}

\e{\rom{Track efficiency}=\fr{\rom{Number of matched tracks}}{\rom{Number of tracks}}}

\e{\label{trackfakerate}\rom{Track fake rate}=\fr{\rom{Number of fake tracks}}{\rom{Number of tracks}}}

The target track fake rate should be much less than 10 $\%$.

\e{\label{trackduplicaterate}\rom{Track duplicate rate}=\fr{\rom{Number of duplicate tracks}}{\rom{Number of tracks}}}

The target track duplicate rate should be 50 $\%$ or less.

\e{\rom{Average duplicate seed number}=\fr{\rom{Number of matched seeds}-\rom{Number matched particles}}{\rom{Number of matched particles}}}

\subsection{\label{spnfuad}Simulation Parameters}

These are the most significant simulation parameters. Some are held constant. The variable parameters are optimized.

\begin{enumerate}
\item Pileup [\#]: The number of soft processes to simulate alongside one hard process.
\item CMS Energy [GeV]: The center of mass energy of the symmetric pp collision.
\item QCD parameters: The QCD parameters to put into the event generator. Always ``Top:qqbar2ttbar=on''.
\item Gaussian Vertex $\sigma$ [$\sigma_t$, $\sigma_x$, $\sigma_y$, $\sigma_z$]: The standard deviation of the gaussian vertex from the center of the coordinate system (x,y,z) = (0,0,0). Always (5 ns, 0.0125 mm, 0.0125 mm, 55.5 mm).
\item B Field $B_x$,$B_y$,$B_z$ [T,T,T]: The magnetic field. Always 0, 0, 2.
\item Events per sequence [n]: The number of events to simulate per CKF reconstruction algorithm. Always 1.
\item FATRAS particle selection $\pt$ [GeV]: The minimum $\pt$ for FATRAS to propagate a particle. Always 150 MeV.
\item Truth seed $\pt$ [GeV]: The minimum $\pt$ for the truth seed algorithm. Always 1 GeV.
\item Truth seed number of hits [\#]: The minimum number of hits for the seed finder to declare a track.
\item Particle smearing pRel: Always 0.01. The relative momentum resolution used to smear the particle truth information to create track states.
\item Seed finder r: 200 mm. The bin side of the space point grid.
\item Seed finder $\Delta r$ min, max: 29, 52 mm. The min (max) distance in r between two measurements within one seed.
\item Seed finder collision region: -250 to 250 mm. The limiting location of collision region in z.
\item Seed finder z: -2000 mm to 2000 mm. The limiting location of measurements.
\item Seed finder max seeds per middle space point: 0. The number of middle space points that can be assigned per space point.
\item Seed finder max cot theta: 5.16. Maximum cot theta angle.
\item Seed finder scattering $\sigma$: 46.312. The maximum number of sigmas of scattering angle that should be searched.
\item Seed finder pT range: 500 MeV to 25.4 GeV. The min (max) pt range of scattering.
\item Seed finder b Field in Z direction: 1.99724 T. B field in z direction.
\item Seed finder impact radius max: 0.19345. The max impact parameter to search.
\item Track parameter estimation delta R: 10 mm, 100 mm. The min (max) deltaR between space points in a seed.
\item CKF minimum $\pt$: 1 GeV. The minimum pT of a track required in order to consider the track for efficiency measurements.
\item CKF minimum number of measurements: 6. The minimum number of hits in a track required in order to consider the track for efficiency measurements.
\end{enumerate}

\subsection{\label{b87dfa0}Optimization}
\section{Results}
\subsection{Default parameters}
\figtab{l l}{Max \textrm{cot}($\theta$) [\textrm{cot}($\theta$)] & 7.406\\
Max $\Delta R$ [mm] & 60.0\\
Min $\Delta R$ [mm]  & 1.0\\
Max $r_\textrm{impact}$ [mm] & 3.0\\
Max scattering $p_{\textrm{T}}$ [GeV] & 10.0\\
Max Seeds Per Middle Space Point [n] & 1\\
Radiation Length Per Seed [\%/100] & 0.1\\
Scattering $\sigma$ [$\sigma$] & 50
}{\label{192837a}Initial parameters.}
\figtab{l l}{
Particle efficiency &0.982273\\
Particle fake rate &0.00065096\\
Particle duplicate rate &0.772914\\
Track efficiency &0.862905\\
Track fake rate &0.00199404\\
Track duplicate rate &0.812663
}{Efficiencies calculated from N ACTS sequence, 100 events per sequence, 100 pileup per event.}
\figpic{9cm}{4.png}{Efficiency plots as function of $\eta$, $\phi$, and $\pt$}
\subsection{$\eta$ from -3 to 3}
The score function is
\e{Score = particle efficiency - cur_fakerate_tracks - cur_duplicaterate_tracks / 5 - cur_runtime / 5}
\figtab{l l}{
Max \textrm{cot}($\theta$) [\textrm{cot}($\theta$)] & 7.999982642 $\pm$ 1.551268963\\
Max $\Delta R$ [mm] & 96.55565929 $\pm$ 84.71230109\\
Min $\Delta R$ [mm]  & 14.49822582 $\pm$ 3.979233489\\
Max $r_\textrm{impact}$ [mm] & 7.204453723 $\pm$ 8.598550912\\
Max scattering $p_{\textrm{T}}$ [GeV] & 23.05472119 $\pm$ 14.2070444\\
Max Seeds Per Middle Space Point [n] & 0 $\pm$0\\
Radiation Length Per Seed & 0.04088986151 $\pm$ 0.0202557741\\
Scattering $\sigma$ [$\sigma$] & 19.67420817 $\pm$ 7.811039786\\
}{Optimized parameters.}
\subsection{$\eta$ from -3 to 3, Efficiency Only}
100 trials. The score function is
\e{score=efficiency}
\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Plot of score per trial.}
\figpic{9cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/parameter_per_trial/grid.png}{Parameters per trial.}
\figpic{9cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/efficiency_per_trial/grid.png}{Efficiency per trial.}
For the best trial,
\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/grid.png}{Efficiency using the optimized parameters.}
\subsection{$\eta$ from 1.5 to 3, Efficiency only}
The score function is 
\e{score=efficiency}
\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Plot of score per trial}
\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/parameter_per_trial/grid.png}{Parameters per trial.}
\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/efficiency_per_trial/grid.png}{Efficiency per trial.}
For the best trial,
\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/grid.png}{Efficiency using the optimized parameters.}
\subsection{$\eta$ from -1.5 to 1.5, Efficiency only}
The score function is 
\e{score=efficiency}
\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/score.png}{Plot of score per trial}
\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/parameter_per_trial/grid.png}{Parameters per trial.}
\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/efficiency_per_trial/grid.png}{Efficiency per trial.}
For the best trial,
\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/grid.png}{Efficiency using the optimized parameters.}
\subsection{$\eta$ from -3 to 3, custom score}
The score function is 
\e{score=eff_particles - fakerate_tracks - duplicaterate_tracks / 5}
\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/score.png}{Plot of score per trial}
\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/parameter_per_trial/grid.png}{Parameters per trial.}
\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/efficiency_per_trial/grid.png}{Efficiency per trial.}
For the best trial,
\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/grid.png}{Efficiency using the optimized parameters.}
\subsection{$\eta$ from -3 to 3, custom score}
The score function is 
\e{score=particle eff - track eff / 2 - track duplicates / 4}
\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/score.png}{Plot of score per trial}
\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/parameter_per_trial/grid.png}{Parameters per trial.}
\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/efficiency_per_trial/grid.png}{Efficiency per trial.}
For the best trial,
\figpic{9cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/grid.png}{Efficiency using the optimized parameters.}
\end{document}

% \figpic{7cm}{2023-01-13-00-07-47/Particle efficiency.png}{Particle efficiency when using $\eta$ from -1 to 1.}
% \figpic{7cm}{2023-01-13-00-07-47/Track duplicate rate.png}{Track duplicate rate when using $\eta$ from -1 to 1.}
% \figpic{7cm}{2023-01-13-00-07-47/Track fake rate.png}{Track fake rate when using $\eta$ from -1 to 1.}
% \subsection{Full $\eta$ Range}
% 100 trials of \ttbar event in the ODD were simulated, and reconstructed using the CKF. This table shows the optimizer's parameters after 100 trials.
% These plots show the change in reconstruction performance per trial.
% \figpic{7cm}{score.png}{Plot of \eqref{score}, the score of each trial during optimization. This shows the optimizer is successfully increasing the score of each trial.}
% \figpic{7cm}{Particle efficiency.png}{Plot of \eqref{eff}, the particle efficiency as a function of number of trials.}
% \figpic{7cm}{Track fake rate.png}{Plot of \eqref{trackfakerate}, the track fake rate as a function of number of trials.}
% \figpic{7cm}{Track duplicate rate.png}{Plot of \eqref{trackduplicaterate}, the track duplicate rate as a function of number of trials.}
% These plots show the change in reconstruction parameters per trial.
% \figpic{7cm}{cotThetaMax.png}{cotThetaMax}
% \figpic{7cm}{deltaRMax.png}{deltaRMax}
% \figpic{7cm}{deltaRMin.png}{deltaRMin}
% \figpic{7cm}{impactMax.png}{impactMax}
% \figpic{7cm}{maxPtScattering.png}{maxPtScattering}
% \figpic{7cm}{maxSeedsPerSpM.png}{maxSeedsPerSpM}
% \figpic{7cm}{radLengthPerSeed.png}{radLengthPerSeed}
% \figpic{7cm}{sigmaScattering.png}{sigmaScattering}
% For simulated \ttbar events, the CKF tracking reconstruction efficiency goes from 80\% near 10 GeV $\pt$~to 65\% near 80 GeV $\pt$. The tracking efficiency as a function of $|\eta|$ is 80\% near $|\eta|$=0, and falls to 50\% near $|\eta|$=3. The tracking efficiency appears uncorrelated as a function of coordinate $\phi$.
% \section{Discussion}
% The performance of the CKF reconstruction without any optimization of initial parameters will be used to benchmark further studies that attempt to optimize the seeding and tracking parameters.
% \section{Conclusion}
% \ttbar events were simulated using Pythia, and evaulated using the ACTS Combinatorial Kalman Filter. Future studies will run optimization algorithms on the ACTS tracking parameters to improve tracking performance.
% \section{Appendix}
% \subsection{List of Symbols}
% \begin{center}
% \begin{tabular}{l l}
% Symbol & Description\\
% B & Magnetic Field [T]\\
% \pt & Transverse momentum [eV]
% \end{tabular}
% \end{center}
% Using the parameters in and the optimization procedure in the optimized parameters are found. The efficiency plots as function of eta, phi, and pt use as parameters the CKF minimum pt and minimum number of measurements.

### 2023-02-28 py/get_denominator.py
Update png functions

@@ -1,5 +1,0 @@
-import ROOT
-
-# Get plot of total number of events as function of eta, phi, pt
-def get_denominator_png(root_path):
-    

### 2023-02-28 py/get_n.py

@@ -1,0 +1,14 @@
+import ROOT
+    
+def get_n_keys():
+    return ['nMeasurements_vs_eta', 'nMeasurements_vs_pT']
+
+# Get plot of total number of events as function of eta, phi, pt
+def get_n_png(root_path):
+    tfile = ROOT.TFile.Open(str(root_path))
+
+    for key in get_n_keys():
+        tprofile = tfile.Get(key)
+        tcanvas = ROOT.TCanvas()
+        tprofile.Draw()
+        tcanvas.Print(str(root_path.parent / (key + '.png')))

### 2023-02-28 py/get_numerator.py

@@ -47,6 +47,7 @@ def get_numerator_pngs_multiple(paths, labels):
 
 def get_numerator_pngs_single(path):
     tfile = ROOT.TFile.Open(path)
+
     efficiency_keys = get_efficiency_keys()
 
     for key in efficiency_keys:
@@ -54,7 +55,5 @@ def get_numerator_pngs_single(path):
         totalhistogram = tefficiency.GetTotalHistogram()
         tcanvas = ROOT.TCanvas()
         tcanvas.SetCanvasSize(2000, 500)
-        ttext = ROOT.TText()
         totalhistogram.Draw()
-        ttext.DrawTextNDC(0.05, 0, path)
         tcanvas.Print(key + '.png')

### 2023-02-28 py/get_png_grid.py

@@ -7,15 +7,13 @@ from PIL import Image
 # filestr_list: list of strings of paths to pngs
 # n: number of images to be placed along x
 # filestr: output file string without extension
-def get_png_grid(dirpath, n):
-    files = os.listdir(dirpath)
-    files_full = [dirpath / f for f in files]
-    images = [Image.open(f) for f in files_full]
+def get_png_grid(dirpath, files_fullpath, output, n):
+    images = [Image.open(f) for f in files_fullpath]
     widths, heights = zip(*(i.size for i in images))
 
     width = widths[0]
     height = heights[0]
-    num_y = ((len(files) - (len(files) % n)) / n)
+    num_y = ((len(files_fullpath) - (len(files_fullpath) % n)) / n)
     new_im = Image.new('RGB', (int(width * n), int(height * num_y)))
 
     for i, im in enumerate(images):
@@ -23,4 +21,16 @@ def get_png_grid(dirpath, n):
         y_offset = int(height * ((i - (i % n)) / n))
         new_im.paste(im, (x_offset, y_offset))
 
-    new_im.save(str(dirpath / 'grid.png'))
+    new_im.save(str(dirpath / output))
+
+def get_png_grid_specific(dirpath):
+    files = os.listdir(dirpath)
+
+    names = ['dup.png', 'fak.png', 'eff.png']
+    dup = ['duplicationRate_vs_eta.png', 'duplicationRate_vs_phi.png', 'duplicationRate_vs_pT.png']
+    fak = ['fakerate_vs_eta.png', 'fakerate_vs_phi.png', 'fakerate_vs_pT.png']
+    eff = ['trackeff_vs_eta.png', 'trackeff_vs_phi.png', 'trackeff_vs_pT.png']
+
+    for i, row in enumerate([dup, fak, eff]):
+        row_full = [dirpath / png for png in row]
+        get_png_grid(dirpath, row_full, names[i], 3)

### 2023-02-28 tex/paper-acts/main.tex
Misc update

@@
 \author{Agustin Romero\thanks{ar1@stanford.edu}}
-
 \newcommand{\pic}[2]{\beg{center}{\includegraphics[height=#1]{#2}}}
-
 \newcommand{\figpic}[3]{
@@
 \end{figure}}
-
+\n{sco}{\rom{score}}
+\n{peff}{\rom{particle efficiency}}
+\n{pdup}{\rom{particle duplicate rate}}
+\n{pfak}{\rom{particle fake rate}}
+\n{teff}{\rom{track efficiency}}
+\n{tdup}{\rom{track duplicate rate}}
+\n{tfak}{\rom{track fak rate}}
+\n{abseta}{$|\eta|<$}
+\n{ttbar}{$t\bar{t}$~}
+\n{qqbar}{$q\bar{q}$~}
+\newcommand{\romax}[0]{_{\textrm{max}}}
+\newcommand{\romin}[0]{_{\textrm{min}}}
+\newcommand{\pt}[0]{p_\textrm{T}}
 \newcommand{\figtab}[3]{
@@
 \end{table}}
-
-\n{abseta}{$|\eta|<$}
-\n{ttbar}{$t\bar{t}$~}
-\n{qqbar}{$q\bar{q}$~}
-\newcommand{\romax}[0]{_{\textrm{max}}}
-\newcommand{\romin}[0]{_{\textrm{min}}}
-\newcommand{\pt}[0]{p_\textrm{T}}
-
 \begin{document}
-
 \maketitle
-
 \section{Introduction}
-
 The purpose of this paper is to fully describe the research to simulate \ttbar collisions in the Open Data Detector, perform vertex and track reconstruction in ACTS, then find parameters that achieve highest tracking efficiency.
 This includes the method of research, results, and discussion on what succeeded and what failed to achieve the research goal.
-
 \section{Background}
-
 ATLAS analyses use \abseta~2.5.
@@
 The goal of this research is to improve the efficiency of tracking and reconstruction, both in accuracy of reconstruction and computational time efficiency.
-
 \subsection{pp at high $|\eta|$}
-
 \subsection{Detector ``transition regtion''}
-
 It is difficult for the CKF algorithm to reconstruct tracks which pass through the barrel strips into the end strips.
-
-\figpic{5cm}{2.png}{Example of a track which passes from the barrel to the end cap. As $|\eta|$ lowers the track's points rightward in this diagram. These tracks are more difficult to reconstruct.}
-
+\figpic{5cm}{2.png}{Diagram of a track which passes from the barrel to the end cap. As $|\eta|$ lowers the track's points rightward in this diagram. These tracks are more difficult to reconstruct.}
 \figpic{5cm}{3.png}{Plot of track fake rate as a function of eta. In the transition region, there is a spike in fake rate, indicating worse performance by the CKF algorithm.}
-
 \section{Method}
-
 The motivation is to apply track reconstruction to separate parts of the detector. One set of parameters was be optimized for the end cap, and another set of parameters for the barrel. 
-
 % \figpic{5cm}{1.png}{Concept of the optimization procedure. Optimize reconstruction parameters for the end cap, and again for the barrel.}
-
 In simulation, scattering events have more simultaneous collisions than soft scattering.
@@
 ``Duplication'' refers to two tracks which are linked to the same particle.
-
-\section{Simulation}
-
 \subsection{Detector}
-
 The magnetic field is a solenoid magnet.
@@
 For historical background, in 2008 the reconstruction algorithms used an interaction region which was Gaussian, 5.6 cm in the beam axis, and 15 $\mu$m transverse to the beam \cite{Piacquadio2008}.
-
 \begin{itemize}
@@
 \end{itemize}
-
 Short strips. Carbon foam body with titanium cooling pipe. The short strip material is divided into the following material.
-
 \begin{itemize}
@@
 \end{itemize}
-
 The long strip material is conventional strip sensors in stereo pairs. The long strip material is divided into the following material.
-
 \begin{itemize}
@@
 
+Some terminology is described here.
 A \ita{sequence} is an ordered list of algorithms beginning at event generation, through CKF reconstruction, and ending at the CKF efficiency analyzer.
-A \ita{trial} is one sequence which generates only one event using one set of parameters.
+A \ita{trial} is one sequence with one set of parameters.
 A \ita{score} is a number calculated given the efficiencies from one trial.
 
-\figtab{l l}{Pileup & 10\\
+\figtab{l l}{Pileup & 100\\
 Vertex x-axis $\sigma$ [mm] & 0.0125\\
@@
 
-% \figtab{l l}{Truth Seed Range $\pt$ [MeV] & 500\\
-% r [mm] & 200\\
-% \Delta r & Optimized from }
+\figtab{l l}{Truth Seed Range $\pt$ [MeV] & 500\\
+r [mm] & 200\\
+\Delta r & Optimized}
 
-The following equations are used to evaluate the performance of the CKF algorithm.
-The default parameters used for tracking is used below.
-Most of these parameters were originally hand tuned.
-Next, they will be optimized.
+The following equations are used to evaluate the performance of the CKF algorithm. The default parameters used for tracking is used below.
 
@@
 
-\qqbar $\rightarrow$ \ttbar events were simulated at energy 14 TeV, with 140 pileup particles, using Pythia, and tracked using ACTS.
-
-The event generator used was Pythia.
+The event generator used was Pythia. \qqbar $\rightarrow$ \ttbar events were simulated at energy 14 TeV, with 100 pileup particles, using Pythia, and tracked using ACTS.
 
@@
 
-These are equations used for evaluating the CKF reconstruction algorithm. Specifically we are interested in \eqref{score}, \eqref{eff}, \eqref{trackfakerate}, and \eqref{trackduplicaterate}.
+These are equations used for evaluating the CKF reconstruction algorithm.
 
@@
 
-\subsection{\label{spnfuad}Simulation Parameters}
+\subsection{\label{spnfuad}Summary of Simulation Parameters}
 
@@
 100 trials. The score function is
-\e{score=efficiency}
+\e{\sco=\peff}
 \figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Plot of score per trial.}
@@
 For the best trial,
-\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/grid.png}{Efficiency using the optimized parameters.}
+\figpic{7cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/dup.png}{Plot of score per trial}
+\figpic{7cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/eff.png}{Parameters per trial.}
+\figpic{7cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/fak.png}{Efficiency per trial.}
 \subsection{$\eta$ from 1.5 to 3, Efficiency only}
 The score function is 
-\e{score=efficiency}
-\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Plot of score per trial}
-\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/parameter_per_trial/grid.png}{Parameters per trial.}
-\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/efficiency_per_trial/grid.png}{Efficiency per trial.}
+\e{\sco=\peff}
+\figpic{6\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Plot of score per trial}
+\figpic{9\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/parameter_per_trial/grid.png}{Parameters per trial.}
+\figpic{9\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/efficiency_per_trial/grid.png}{Efficiency per trial.}
 For the best trial,
-\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/grid.png}{Efficiency using the optimized parameters.}
+\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/dup.png}{Plot of score per trial}
+\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/eff.png}{Parameters per trial.}
+\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/fak.png}{Efficiency per trial.}
 \subsection{$\eta$ from -1.5 to 1.5, Efficiency only}
 The score function is 
-\e{score=efficiency}
+\e{\sco=\peff}
 \figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/score.png}{Plot of score per trial}
@@
 For the best trial,
-\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/grid.png}{Efficiency using the optimized parameters.}
+\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from -3 to 3, custom score}
 The score function is 
-\e{score=eff_particles - fakerate_tracks - duplicaterate_tracks / 5}
+\e{\sco=\preff - \tfak - \tdup/5}
 \figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/score.png}{Plot of score per trial}
@@
 For the best trial,
-\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/grid.png}{Efficiency using the optimized parameters.}
+\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from -3 to 3, custom score}
 The score function is
-\e{score=particle eff - track eff / 2 - track duplicates / 4}
+\e{\sco=\peff - \tfak / 2 -\tdup/4}
 \figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/score.png}{Plot of score per trial}
@@
 For the best trial,
-\figpic{9cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/grid.png}{Efficiency using the optimized parameters.}
+\figpic{7cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{7cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{7cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \end{document}

### 2023-02-28 acts-gun-generic-optuna/main.py

@@ -1,199 +1,35 @@
-#!/usr/bin/env python3
-import sys
-
-import sys
-import os
-import yaml
-import pprint
-import time
-import datetime
-import warnings
-
-import optuna
-import logging
-import uproot
-
-import pathlib
-import matplotlib
-
-matplotlib.use("pdf")
-import matplotlib.pyplot as plt
-import random
-import subprocess
-import multiprocessing
-import numpy as np
-import json
-import array
-import sys
 import argparse
-import pandas as pd
-
-from typing import Optional, Union
-from pathlib import Path
-
-from optuna.visualization import plot_contour
-from optuna.visualization import plot_edf
-from optuna.visualization import plot_intermediate_values
-from optuna.visualization import plot_optimization_history
-from optuna.visualization import plot_parallel_coordinate
-from optuna.visualization import plot_param_importances
-from optuna.visualization import plot_slice
-
-srcDir = Path(__file__).resolve().parent
-curDir = Path(os.getcwd())
-
-def run_ckf(params, names, outDir):
-
-    if len(params) != len(names):
-        raise Exception("Length of Params must equal names")
-
-    ckf_script = srcDir / "ckf.py"
-    nevts = "--nEvents=1"
-    indir = "--indir=" + str(curDir)
-    outdir = "--output=" + str(outDir)
-
-    ret = ["python"]
-    ret.append(ckf_script)
-    ret.append(nevts)
-    ret.append(indir)
-    ret.append(outdir)
-
-    i = 0
-    for param in params:
-        arg = "--sf_" + names[i] + "=" + str(param)
-        ret.append(arg)
-        i += 1
-
-    # Run CKF for the given parameters
-    subprocess.call(ret)
-
-
-class Objective:
-    def __init__(self, k_dup, k_time):
-        self.res = {
-            "eff": [],
-            "fakerate": [],
-            "duplicaterate": [],
-            "runtime": [],
-        }
-
-        self.k_dup = k_dup
-        self.k_time = k_time
-
-    def __call__(self, trial):
-        params = []
-
-        maxSeedsPerSpM = trial.suggest_int("maxSeedsPerSpM", 0, 10)
-        params.append(maxSeedsPerSpM)
-        cotThetaMax = trial.suggest_float("cotThetaMax", 5.0, 10.0)
-        params.append(cotThetaMax)
-        sigmaScattering = trial.suggest_float("sigmaScattering", 0.2, 50)
-        params.append(sigmaScattering)
[…]

### 2023-02-28 os/arch/user.js

@@ -68,4 +68,5 @@ user_pref("toolkit.telemetry.shutdownPingSender.enabled", false);
 user_pref("toolkit.telemetry.unified", false);
 user_pref("toolkit.telemetry.unifiedIsOptIn", false);
 user_pref("toolkit.telemetry.updatePing.enabled", false);
-user_pref("ui.key.accelKey", 91);
+user_pref("browser.tabs.tabmanager.enabled", false);
+

### 2023-02-28 sh/dl.sh

@@ -1,12 +1,15 @@
-baseurl="https://webcast.in2p3.fr"
+# get the pdf fles from the page
+
+url=$@
+
+curl -o firstpage "$url"
+sed -i -e '/\.pdf/!d' firstpage
+grep -oP '(?<=href=").*(?=">)' firstpage > secondpage
+
+dlbase="https://nsarchive2.gwu.edu/nsa/cuba_mis_cri/"
 
 while read -r line; do
 echo "Downloading ${line}"
-curl -o firstpage "${baseurl}/video/${line}"
-sed -i -e '/\/player\//!d' firstpage
-video=$(grep -oP '(?<=player/).*(?=\?)' firstpage)
-curl -o secondpage "${baseurl}/player/${video}"
-sed -i -e '/stripSlash/!d' secondpage
-mpfour=$(grep -oP '(?<=").*(?=")' secondpage)
-curl -o "${line}.mp4" -L --limit-rate 800k "${baseurl}${mpfour}"
-done < dl
+wget --limit-rate 1M "${dlbase}/${line}"
+sleep 10
+done < secondpage

### 2023-02-28 tex/paper-acts/main.tex
Progress updating paper

@@
 \usepackage[backend=bibtex]{biblatex}
+\geometry{top=0.75in, bottom=1in, left=0.75in, right=0.75in}
 \addbibresource{bib.bib}
@@
 \n{tfak}{\rom{track fak rate}}
+\n{runtime}
 \n{abseta}{$|\eta|<$}
@@
 ATLAS analyses use \abseta~2.5.
-After the HL-LHC upgrade, ATLAS will use \abseta~4.
+After the HL-LHC upgrade, analyses may use \abseta~4.
 The goal of this research is to improve the efficiency of tracking and reconstruction, both in accuracy of reconstruction and computational time efficiency.
-\subsection{pp at high $|\eta|$}
+% \subsection{pp at high $|\eta|$}
 \subsection{Detector ``transition regtion''}
@@
 r [mm] & 200\\
-\Delta r & Optimized}
+$\Delta$ r & Optimized}
 
@@
 
-\subsection{Kalman Filter algorithm}
+% \subsection{Kalman Filter algorithm}
 
@@
 
-\subsection{Track fitting}
+% \subsection{Track fitting}
 
@@
 \end{enumerate}
-
 \subsection{\label{b87dfa0}Optimization}
+The procedure for optimization is
+\begin{enumerate}
+\item Initialize the optimizer and set the first trial paremters to \fref{192837a}.
+\item Run N trials using the following steps.
+\begin{enumerate}
+\item Run one ACTS sequence with one event generated in the ODD.:
+\begin{enumerate}
+\item Pythia8, with multiple pileup particles.
+\item GEANT+Fatras with the ODD.
+\item Digitization with ACTS.
+\item Seeding with ACTS.
+\item CKF track reconstruction wth ACTS.
+\end{enumerate}
+\item Calculate the score, calculate new parameters.
+\end{enumerate}
+\item Report the N trials, their parameters, and the score of each trial.
+\end{enumerate}
 \section{Results}
@@
 Max $r_\textrm{impact}$ [mm] & 3.0\\
-Max scattering $p_{\textrm{T}}$ [GeV] & 10.0\\
+Max scattering $\pt$ [GeV] & 10.0\\
 Max Seeds Per Middle Space Point [n] & 1\\
@@
 Track duplicate rate &0.812663
-}{Efficiencies calculated from N ACTS sequence, 100 events per sequence, 100 pileup per event.}
-\figpic{9cm}{4.png}{Efficiency plots as function of $\eta$, $\phi$, and $\pt$}
-\subsection{$\eta$ from -3 to 3}
+}{Initial efficiencies calculated from 1 ACTS sequence, with 100 events, with 100 pileup particles per event.}
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/dup.png}{Initial track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/eff.png}{Initial track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/fak.png}{Initial track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
+\subsection{$\eta$ from -3 to 3, custom score}
 The score function is
-\e{Score = particle efficiency - cur_fakerate_tracks - cur_duplicaterate_tracks / 5 - cur_runtime / 5}
+\e{\sco = \preff - \tfak - \tdup / 5 - \runtime / 5}
 \figtab{l l}{
@@
 \subsection{$\eta$ from -3 to 3, Efficiency Only}
-100 trials. The score function is
+The score function is
 \e{\sco=\peff}
+\figtab{l l}{
+Max \textrm{cot}($\theta$) [\textrm{cot}($\theta$)] & 9.97960491147606\\
+Max $\Delta R$ [mm] & 193.7852042641601\\
+Min $\Delta R$ [mm]  & 6.186148583682443\\
+Max $r_\textrm{impact}$ [mm] & 5.3520710118467525\\
+Max scattering $p_{\textrm{T}}$ [GeV] & 6.270284198944674\\
+Max Seeds Per Middle Space Point [n] & 6\\
+Radiation Length Per Seed & 0.0012607157984066096\\
+Scattering $\sigma$ [$\sigma$] & 40.60867756209729
+}{Optimized parameters.}
 \figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Plot of score per trial.}
@@
 \figpic{9cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/efficiency_per_trial/grid.png}{Efficiency per trial.}
-For the best trial,
-\figpic{7cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/dup.png}{Plot of score per trial}
-\figpic{7cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/eff.png}{Parameters per trial.}
-\figpic{7cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/fak.png}{Efficiency per trial.}
+The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
+\figpic{4cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from 1.5 to 3, Efficiency only}
@@
 \e{\sco=\peff}
+\figtab{l l}{
+Max \textrm{cot}($\theta$) [\textrm{cot}($\theta$)] & 9.955015534804646\\
+Max $\Delta R$ [mm] & 92.55025939304613\\
+Min $\Delta R$ [mm] & 4.954090296295913\\
+Max $r_\textrm{impact}$ [mm] & 6.220456981531933\\
+Max scattering $p_{\textrm{T}}$ [GeV] & 25.742954905376422\\
+Max Seeds Per Middle Space Point [n] & 9\\
+Radiation Length Per Seed & 0.050182305379654776\\
+Scattering $\sigma$ [$\sigma$] & 41.62774067749547 
+}{Optimized parameters.}
 \figpic{6\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Plot of score per trial}
@@
 \figpic{9\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/efficiency_per_trial/grid.png}{Efficiency per trial.}
-For the best trial,
-\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/dup.png}{Plot of score per trial}
-\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/eff.png}{Parameters per trial.}
-\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/fak.png}{Efficiency per trial.}
+The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from -1.5 to 1.5, Efficiency only}
@@
 \e{\sco=\peff}
+\figtab{l l}{
+Max \textrm{cot}($\theta$) [\textrm{cot}($\theta$)] & 8.585756197102755\\
+Max $\Delta R$ [mm] & 226.44349889012312\\
+Min $\Delta R$ [mm] & 13.667849506894473\\
+Max $r_\textrm{impact}$ [mm] & 21.905395073424017\\
+Max scattering $p_{\textrm{T}}$ [GeV] & 49.44440486374715\\
+Max Seeds Per Middle Space Point [n] & 10\\
+Radiation Length Per Seed & 0.029552672847034882\\
+Scattering $\sigma$ [$\sigma$] & 17.750322166919286 
+}{Optimized parameters.}
 \figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/score.png}{Plot of score per trial}
@@
 \figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/efficiency_per_trial/grid.png}{Efficiency per trial.}
-For the best trial,
-\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
+The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from -3 to 3, custom score}
@@
 \figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/efficiency_per_trial/grid.png}{Efficiency per trial.}
-For the best trial,
-\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
+The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from -3 to 3, custom score}
@@
 \figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/efficiency_per_trial/grid.png}{Efficiency per trial.}
-For the best trial,
-\figpic{7cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{7cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{7cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
+The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
+\figpic{4cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{4cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \end{document}

### 2023-03-01 js/cleanup.py
Add js

@@ -1,0 +1,23 @@
+# Delete .png files that are not in nodes.json.
+
+import json
+import random
+import string
+import os
+
+files = os.listdir('./')
+
+def ends_with_png(s):
+    return s.endswith('png')
+
+files_png = filter(ends_with_png, files)
+
+nodes_file = open('./nodes.json', 'r')
+nodes_json = json.load(nodes_file)
+
+for file_png in files_png:
+    if file_png not in nodes_json:
+        print(file_png, 'not in json, deleting.')
+        os.unlink(file_png)
+
+nodes_file.close()

### 2023-03-01 js/deleter.js

@@ -1,0 +1,37 @@
+'use strict'
+
+const fs = require('fs')
+
+function delete_node(node) {
+    const nodes_file = fs.readFileSync('./public/nodes.json')
+    var nodes_dict = JSON.parse(nodes_file.toString())
+
+    if (node in nodes_dict) {
+	console.log('Deleting node', node)
+	delete nodes_dict[node]
+	fs.writeFileSync('./public/nodes.json', JSON.stringify(nodes_dict))
+    }
+
+    if (fs.existsSync('./public/' + node + '.json') ) {
+	console.log('Deleting json', node)
+	fs.unlinkSync('./public/' + node + '.json')
+    }
+
+    if (fs.existsSync('./public/' + node)) {
+	console.log('Deleting png', node)
+	fs.unlinkSync('./public/' + node)
+    }
+}
+
+function receive_deletes(app) {
+    app.post('/delete', function (req, res) {
+	if (req.body.prompt == 'greenchickadee') {
+	    delete_node(req.body.node)
+	}
+	res.sendStatus(200);
+    })
+}
+
+module.exports = {
+    receive_deletes: receive_deletes
+}

### 2023-03-01 js/edger.js

@@ -1,0 +1,24 @@
+'use strict'
+
+const fs = require('fs')
+
+function edge_node(edge_from_node, to_list) {
+    var filename = './public/edges.json'
+    var edgesfile = fs.readFileSync(filename)
+    var edges_dict = JSON.parse(edgesfile.toString())
+    edges_dict[edge_from_node] = to_list
+    fs.writeFileSync(filename, JSON.stringify(edges_dict))
+}
+
+function receive_edges(app) {
+    app.post('/edge', function (req, res) {
+	if (req.body.prompt == 'greenchickadee') {
+	    edge_node(req.body.edge_from_node, req.body.to_list)
+	}
+	res.sendStatus(200);
+    })
+}
+
+module.exports = {
+    receive_edges: receive_edges
+}

### 2023-03-01 js/editor.js

@@ -1,0 +1,16 @@
+'use strict'
+
+const fs = require('fs')
+
+function receive_edits(app) {
+    app.post('/edit', function (req, res) {
+	if (req.body.prompt == 'greenchickadee') {
+	    fs.writeFileSync('./public/' + req.body.page + '.json', JSON.stringify(req.body.path_list))
+	    res.sendStatus(200);
+	}
+    })
+}
+
+module.exports = {
+    receive_edits: receive_edits
+}

### 2023-03-01 js/mover.js

@@ -1,0 +1,24 @@
+'use strict'
+
+const fs = require('fs')
+
+function move_node(node, coordinate) {
+    const nodesfile = fs.readFileSync('./public/nodes.json')
+    var nodes_json = JSON.parse(nodesfile.toString())
+    nodes_json[node] = coordinate
+    nodes_json['last'] = coordinate
+    fs.writeFileSync('./public/nodes.json', JSON.stringify(nodes_json))
+}
+
+function receive_moves(app) {
+    app.post('/move', function (req, res) {
+	if (req.body.prompt == 'greenchickadee') {
+	    move_node(req.body.node, req.body.coordinate)
+	}
+	res.sendStatus(200);
+    })
+}
+
+module.exports = {
+    receive_moves: receive_moves
+}

### 2023-03-01 js/node.js

@@ -1,0 +1,26 @@
+"use strict";
+
+const express = require('express')
+const app = express()
+app.use(express.json({limit: '50mb'}));
+
+const server = require('./server.js')
+server.serve_files(app, express)
+
+const mover = require('./mover.js')
+mover.receive_moves(app)
+
+const deleter = require('./deleter.js')
+deleter.receive_deletes(app)
+
+const edger = require('./edger.js')
+edger.receive_edges(app)
+
+const editor = require('./editor.js')
+editor.receive_edits(app)
+
+const port = 8001
+
+app.listen(port, () => {
+    console.log(`Listening on port ${port}.`)
+})

### 2023-03-01 js/public/index.js

@@ -1,0 +1,267 @@
+var edge_first_node = ''
+var bool_move_node = false
+var bool_make_edge = false
+var bool_move_connected_nodes = false
+var bool_delete_edge = false
+var bool_mobile = /iPhone|iPad/i.test(navigator.userAgent);
+var move_node_names = []
+var move_node_initial_coordinates = []
+
+function set_json(url, payload) {
+    var request = new XMLHttpRequest()
+    request.open('POST', url, false)
+    request.setRequestHeader('Content-Type', 'application/json')
+    request.send(JSON.stringify(payload))
+}
+
+function get_json(url) {
+    var request = new XMLHttpRequest()
+    request.open('GET', url, false)
+    request.send(null)
+    return JSON.parse(request.responseText)
+}
+
+var nodes = get_json('/nodes.json')
+var edges = get_json('/edges.json')
+
+function delete_node(nodename) {
+    payload = {
+        node: nodename
+    }
+
+    set_json('/delete', payload)    
+}
+
+function move_node(nodename, coordinate) {
+    payload = {
+        node: nodename,
+	coordinate: coordinate
+    }
+
+    set_json('/move', payload)
+}
+
+function edge_node(nodename, to_node_list) {
+    payload = {
+	from_node: nodename,
+	to_node_list: to_node_list
+    }
+
+    set_json('/edge', payload)
+}
+
+async function update() {
+    nodes = get_json('/nodes.json')
+    edges = get_json('/edges.json')
+    draw()
+}
+
+function stop_dragging(node) {
+    bool_move_node = false
+    move_node_names = []
+    move_node_initial_coordinates = []
+    deck_object.setProps({controller: true})
+}
+
+function set_move_node_names(parent_node) {
+    var move_node_queue = []
+
+    if (parent_node in edges) {
+	move_node_queue = edges[parent_node]
+    }
+
+    while (move_node_queue.length > 0) {
+	var next_node = move_node_queue.shift()
+	if (!(move_node_names.includes(next_node))) {
+	    move_node_names.push(next_node)
+	    move_node_initial_coordinates.push(nodes[next_node])
+	    if (next_node in edges) {
+		move_node_queue.push(...edges[next_node])
+	    }
+	}
+    }
+}
+
+function gettooltip({object}) {
[…]

### 2023-03-01 js/server.js

@@ -1,0 +1,9 @@
+'use strict'
+
+function serve_files(app, express) {
+    app.use('/', express.static('public'));
+}
+
+module.exports = {
+    serve_files: serve_files
+}

### 2023-03-01 js/public/index.js
Update js

@@ -1,18 +1,28 @@
-var edge_first_node = ''
-var bool_move_node = false
+var bool_delete_edge = false
+var bool_draw = false
 var bool_make_edge = false
 var bool_move_connected_nodes = false
-var bool_delete_edge = false
-var bool_mobile = /iPhone|iPad/i.test(navigator.userAgent);
-var move_node_names = []
-var move_node_initial_coordinates = []
-
-function set_json(url, payload) {
-    var request = new XMLHttpRequest()
-    request.open('POST', url, false)
-    request.setRequestHeader('Content-Type', 'application/json')
-    request.send(JSON.stringify(payload))
-}
+var bool_scroll = false
+var bool_tooltip = false
+var bool_mobile = /iPad/i.test(navigator.userAgent)
+var current_page = ''
+var drag_first_y = 0
+var edge_first_node = ''
+var edit_timeout_id = 0
+var move_nodes = []
+var edge_nodes = []
+var pages = {}
+var draw_scale = 1
+var canvas = document.getElementById('page')
+canvas.width = window.innerWidth
+canvas.height = window.innerHeight
+canvas.style.width = canvas.width + "px"
+canvas.style.height = canvas.height + "px"
+canvas.width = canvas.width * window.devicePixelRatio
+canvas.height = canvas.height * window.devicePixelRatio
+var context = canvas.getContext('2d')
+var original_transform = context.getTransform()
+context.lineWidth = 3
 
 function get_json(url) {
     var request = new XMLHttpRequest()
@@ -21,8 +31,18 @@ function get_json(url) {
     return JSON.parse(request.responseText)
 }
 
-var nodes = get_json('/nodes.json')
-var edges = get_json('/edges.json')
+async function get_graph_data() {
+    nodes = get_json('/nodes.json')
+    edges = get_json('/edges.json')
+    draw_graph()
+}
+
+function set_json(url, payload) {
+    var request = new XMLHttpRequest()
+    request.open('POST', url, false)
+    request.setRequestHeader('Content-Type', 'application/json')
+    request.send(JSON.stringify(payload))
+}
 
 function delete_node(nodename) {
     payload = {
@@ -32,49 +52,38 @@ function delete_node(nodename) {
     set_json('/delete', payload)    
 }
 
-function move_node(nodename, coordinate) {
[…]

### 2023-03-01 tex/paper-acts/main.tex
update paper, js

@@
 \end{figure}}
-\n{sco}{\rom{score}}
-\n{peff}{\rom{particle efficiency}}
-\n{pdup}{\rom{particle duplicate rate}}
-\n{pfak}{\rom{particle fake rate}}
-\n{teff}{\rom{track efficiency}}
-\n{tdup}{\rom{track duplicate rate}}
-\n{tfak}{\rom{track fak rate}}
-\n{runtime}
+\n{sco}{\rom{Score}}
+\n{peff}{\rom{Particle Efficiency [frac]}}
+\n{pdup}{\rom{Particle Duplicates [frac]}}
+\n{pfak}{\rom{Particle Fakes [frac]}}
+\n{teff}{\rom{Track Efficiency [frac]}}
+\n{tdup}{\rom{Track Duplicates [frac]}}
+\n{tfak}{\rom{Track Fakes [frac]}}
+\n{runtime}{\rom{Runtime [s]}}
 \n{abseta}{$|\eta|<$}
@@
 
-Some terminology is described here.
-A \ita{sequence} is an ordered list of algorithms beginning at event generation, through CKF reconstruction, and ending at the CKF efficiency analyzer.
-A \ita{trial} is one sequence with one set of parameters.
-A \ita{score} is a number calculated given the efficiencies from one trial.
-
 \figtab{l l}{Pileup & 100\\
@@
 
-\figtab{l l}{Truth Seed Range $\pt$ [MeV] & 500\\
-r [mm] & 200\\
-$\Delta$ r & Optimized}
+% \figtab{l l}{Truth Seed Range $\pt$ [MeV] & 500\\
+% r [mm] & 200\\
+% $\Delta$ r & Optimized}{}
 
@@
 \begin{enumerate}
-\item Initialize the optimizer and set the first trial paremters to \fref{192837a}.
+\item Initialize the optimizer and set the first trial paremters to \tref{192837a}.
 \item Run N trials using the following steps.
@@
 }{Initial efficiencies calculated from 1 ACTS sequence, with 100 events, with 100 pileup particles per event.}
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/dup.png}{Initial track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/eff.png}{Initial track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/fak.png}{Initial track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/dup.png}{Initial track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/eff.png}{Initial track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/fak.png}{Initial track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from -3 to 3, custom score}
 The score function is
-\e{\sco = \preff - \tfak - \tdup / 5 - \runtime / 5}
+\e{\sco = \peff - \tfak - \tdup / 5 - \runtime / 5}
 \figtab{l l}{
@@
 Max scattering $p_{\textrm{T}}$ [GeV] & 23.05472119 $\pm$ 14.2070444\\
-Max Seeds Per Middle Space Point [n] & 0 $\pm$0\\
+Max Seeds Per Middle Space Point [n] & 0 $\pm$ 0\\
 Radiation Length Per Seed & 0.04088986151 $\pm$ 0.0202557741\\
@@
 }{Optimized parameters.}
+This optimization was run 7 separate times, 100 trials each, to test how large the uncertainties are on the best trial parameters. No efficiency plots are shown.
 \subsection{$\eta$ from -3 to 3, Efficiency Only}
@@
 }{Optimized parameters.}
-\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Plot of score per trial.}
+\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Optimizer score per trial..}
 \figpic{9cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/parameter_per_trial/grid.png}{Parameters per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/efficiency_per_trial/grid.png}{Efficiency per trial.}
-The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
-\figpic{4cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
+The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.
+\figpic{3.5cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from 1.5 to 3, Efficiency only}
@@
 }{Optimized parameters.}
-\figpic{6\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Plot of score per trial}
-\figpic{9\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/parameter_per_trial/grid.png}{Parameters per trial.}
-\figpic{9\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/efficiency_per_trial/grid.png}{Efficiency per trial.}
-The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Optimizer score per trial.}
+\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/parameter_per_trial/grid.png}{Parameters per trial.}
+\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/efficiency_per_trial/grid.png}{Efficiency per trial.}
+The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from -1.5 to 1.5, Efficiency only}
@@
 }{Optimized parameters.}
-\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/score.png}{Plot of score per trial}
+\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/score.png}{Optimizer score per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/parameter_per_trial/grid.png}{Parameters per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/efficiency_per_trial/grid.png}{Efficiency per trial.}
-The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
+The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from -3 to 3, custom score}
 The score function is 
-\e{\sco=\preff - \tfak - \tdup/5}
-\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/score.png}{Plot of score per trial}
+\e{\sco=\peff - \tfak - \tdup/5}
+\figtab{l l}{
+Max \textrm{cot}($\theta$) [\textrm{cot}($\theta$)] & 9.894147867588261\\
+Max $\Delta R$ [mm] & 78.45827959526429\\
+Min $\Delta R$ [mm] & 22.770804208643327\\
+Max $r_\textrm{impact}$ [mm] & 17.264025370752\\
+Max scattering $p_{\textrm{T}}$ [GeV] & 22.138871404772974\\
+Max Seeds Per Middle Space Point [n] & 7\\
+Radiation Length Per Seed & 0.001526817277071645\\
+Scattering $\sigma$ [$\sigma$] & 33.877560589074356 
+}{Optimized parameters.}
+\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/score.png}{Optimizer score per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/parameter_per_trial/grid.png}{Parameters per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/efficiency_per_trial/grid.png}{Efficiency per trial.}
-The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
+The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \subsection{$\eta$ from -3 to 3, custom score}
@@
 \e{\sco=\peff - \tfak / 2 -\tdup/4}
-\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/score.png}{Plot of score per trial}
+\figtab{l l}{
+Max \textrm{cot}($\theta$) [\textrm{cot}($\theta$)] & 9.866139016895074\\
+Max $\Delta R$ [mm] & 183.62476842099014\\
+Min $\Delta R$ [mm] & 27.017826961402342\\
+Max $r_\textrm{impact}$ [mm] & 16.705994491748385\\
+Max scattering $p_{\textrm{T}}$ [GeV] & 46.36841479558609\\
+Max Seeds Per Middle Space Point [n] & 10\\
+Radiation Length Per Seed & 0.09965229969028085\\
+Scattering $\sigma$ [$\sigma$] & 1.5604089909909047 
+}{Optimized parameters.}
+\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/score.png}{Optimizer score per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/parameter_per_trial/grid.png}{Parameters per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/efficiency_per_trial/grid.png}{Efficiency per trial.}
-The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
-\figpic{4cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
-\figpic{4cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
+The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.
+\figpic{3.5cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
+\figpic{3.5cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
 \end{document}
@@
 The efficiency plots as function of eta, phi, and pt use as parameters the CKF minimum pt and minimum number of measurements.
+% Some terminology is described here.
+A \ita{sequence} is the ordered list of algorithms beginning at event generation, through particle propagation, CKF reconstruction, and ending at the CKF efficiency analyzer.
+A \ita{trial} is one sequence and one set of parameters.
+A \ita{score} is the number calculated given the efficiencies from one trial.

### 2023-03-01 js/deleter.js

@@ -7,27 +7,22 @@ function delete_node(node) {
     var nodes_dict = JSON.parse(nodes_file.toString())
 
     if (node in nodes_dict) {
-	console.log('Deleting node', node)
 	delete nodes_dict[node]
 	fs.writeFileSync('./public/nodes.json', JSON.stringify(nodes_dict))
     }
 
     if (fs.existsSync('./public/' + node + '.json') ) {
-	console.log('Deleting json', node)
 	fs.unlinkSync('./public/' + node + '.json')
     }
 
     if (fs.existsSync('./public/' + node)) {
-	console.log('Deleting png', node)
 	fs.unlinkSync('./public/' + node)
     }
 }
 
 function receive_deletes(app) {
     app.post('/delete', function (req, res) {
-	if (req.body.prompt == 'greenchickadee') {
-	    delete_node(req.body.node)
-	}
+	delete_node(req.body.node)
 	res.sendStatus(200);
     })
 }

### 2023-03-01 js/edger.js

@@ -1,20 +1,20 @@
 'use strict'
-
 const fs = require('fs')
 
-function edge_node(edge_from_node, to_list) {
+function edge_node(node_list, edge_list) {
     var filename = './public/edges.json'
     var edgesfile = fs.readFileSync(filename)
     var edges_dict = JSON.parse(edgesfile.toString())
-    edges_dict[edge_from_node] = to_list
+
+    for (var i = 0; i < node_list.length; i++) {
+	edges_dict[node_list[i]] = edge_list[i]
+    }
     fs.writeFileSync(filename, JSON.stringify(edges_dict))
 }
 
 function receive_edges(app) {
     app.post('/edge', function (req, res) {
-	if (req.body.prompt == 'greenchickadee') {
-	    edge_node(req.body.edge_from_node, req.body.to_list)
-	}
+	edge_node(req.body.node_list, req.body.edge_list)
 	res.sendStatus(200);
     })
 }

### 2023-03-01 js/editor.js

@@ -4,10 +4,8 @@ const fs = require('fs')
 
 function receive_edits(app) {
     app.post('/edit', function (req, res) {
-	if (req.body.prompt == 'greenchickadee') {
-	    fs.writeFileSync('./public/' + req.body.page + '.json', JSON.stringify(req.body.path_list))
-	    res.sendStatus(200);
-	}
+	fs.writeFileSync('./public/' + req.body.page + '.json', JSON.stringify(req.body.path_list))
+	res.sendStatus(200);
     })
 }
 

### 2023-03-01 js/mover.js

@@ -2,19 +2,21 @@
 
 const fs = require('fs')
 
-function move_node(node, coordinate) {
+function move_node(node_list, xy_list) {
     const nodesfile = fs.readFileSync('./public/nodes.json')
     var nodes_json = JSON.parse(nodesfile.toString())
-    nodes_json[node] = coordinate
-    nodes_json['last'] = coordinate
+
+    for (var i = 0; i < node_list.length; i++) {
+	nodes_json[node_list[i]] = xy_list[i]
+    }
+    
+    nodes_json['last'] = xy_list[0]
     fs.writeFileSync('./public/nodes.json', JSON.stringify(nodes_json))
 }
 
 function receive_moves(app) {
     app.post('/move', function (req, res) {
-	if (req.body.prompt == 'greenchickadee') {
-	    move_node(req.body.node, req.body.coordinate)
-	}
+	move_node(req.body.node_list, req.body.xy_list)
 	res.sendStatus(200);
     })
 }

### 2023-03-03 py/get_time.py
Add function to get plot of runtime

@@ -1,0 +1,41 @@
+from matplotlib import pyplot
+import os
+import pathlib
+import pandas
+import get_figure
+
+def starts_with_trial(s):
+    return s.startswith('trial_')
+
+def get_trial_path_from_str(s, d):
+    return pathlib.Path(d) / s
+
+def get_time_trial(trial_path):
+    timing_path = trial_path / 'timing.tsv'
+    timing = pandas.read_csv(timing_path, sep="\t")
+    time_ckf = float(
+        timing[timing["identifier"].str.match("Algorithm:TrackFindingAlgorithm")][
+            "time_perevent_s"
+        ]
+    )
+    time_seeding = float(
+        timing[timing["identifier"].str.match("Algorithm:SeedingAlgorithm")][
+            "time_perevent_s"
+        ]
+    )
+    cur_runtime = time_ckf + time_seeding
+    return cur_runtime
+
+def get_time(data_dirpath):
+    time_trials = []
+    listdir = os.listdir(data_dirpath)
+    trial_paths = []
+    for dir in listdir:
+        if starts_with_trial(dir):
+            trial_paths.append(data_dirpath / dir)
+            
+    for trial_path in trial_paths:
+        time_trials.append(get_time_trial(trial_path))
+        
+    figure = get_figure.get_study_figure(time_trials, 'Trial', '', 'Run time per trial [s]')
+    pyplot.savefig(data_dirpath / 'time.png', dpi = 200)

### 2023-03-03 tex/paper-acts/main.tex
Add plots of run time per trial.

@@
 }{Optimized parameters.}
-\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Optimizer score per trial..}
+\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Optimizer score per trial.}
+\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/time.png}{Optimizer time per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/parameter_per_trial/grid.png}{Parameters per trial.}
@@
 \figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Optimizer score per trial.}
+\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/time.png}{Optimizer time per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/parameter_per_trial/grid.png}{Parameters per trial.}
@@
 \figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/score.png}{Optimizer score per trial.}
+\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/time.png}{Optimizer time per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/parameter_per_trial/grid.png}{Parameters per trial.}
@@
 \figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/score.png}{Optimizer score per trial.}
+\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/time.png}{Optimizer time per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/parameter_per_trial/grid.png}{Parameters per trial.}
@@
 \figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/score.png}{Optimizer score per trial.}
+\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/time.png}{Optimizer time per trial.}
 \figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/parameter_per_trial/grid.png}{Parameters per trial.}
